Consumption and resistance across states and HRRs

### 2017-03-01 states/resistance/state-report.Rmd
removed wrong bugs

gram_negs = c('Escherichia coli', 'Klebsiella pneumoniae',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Klebisella oxytoca', 'Enterococcus faecium')
gram_poss = c('Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)

@@

>>>>

# swo> I removed Klebsiella because it's mostly in immune-compromised people
# and K. oxytoca because it's from neonatal septicemia?
gram_negs = c('Escherichia coli',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Enterococcus faecium')
gram_poss = c('Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)

@@

#### Linear

```{r}
linear_all_models_result = function(x, this_place) {
  x %>%
    group_by(bug, drug_group) %>%
    do(linear_models(., 'percent_nonsusceptible')) %>%
    ungroup %>%
    filter(!is.na(estimate)) %>%
    mutate(adj.p.value=p.adjust(p.value, method='BH'),
           sig=pvalue_stars(adj.p.value)) %>%
    select(bug, drug_group,
           explanatory, slope=estimate, p.value,
           adj.p.value, sig)
}

linear_all_state_res = linear_all_models_result(state_dat, 'state')
linear_all_hrr_res = linear_all_models_result(hrr_dat, 'hrr')

linear_all_state_res %>% kable
```
